Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-06-23 WRITEUP/ms.tex
combined figures and bigger fonts

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_0.53}.pdf}
  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_0.53}.pdf}

  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_6.81}.pdf}
  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_6.81}.pdf}

  \includegraphics[width=0.49\textwidth]{\figpath/{dual_16_ncut_18.96}.pdf}
  \includegraphics[width=0.49\textwidth]{\figpath/{dual_28_ncut_18.96}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump finder in
\flower during its accreting phase (\Fig{SFH}a), where \flower is dispersion-dominated (left two columns), and 
its quiescent phase, which is rotation-dominated (right two columns).
Leftmost and second left panels show the accreting phase of \flower from different viewing angles. Similarly, for the right two columns
in the quiescent phase.
Colorbar on the right shows the mean H$_2$ number density, weighted by gas mass. 
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. 
\AP{label with the phase should be included in the first row}
\label{fig:MCC}
}
\end{figure*}

>>>>

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_16_ncut_0.53}.pdf} \hspace{-1.2em}
  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_28_ncut_0.53}.pdf}

  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_16_ncut_6.81}.pdf} \hspace{-1.2em}
  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_28_ncut_6.81}.pdf}

  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_16_ncut_18.96}.pdf} \hspace{-1.2em}
  \includegraphics[width=0.495\textwidth]{\figpath/SS_bigfonts/{dual_28_ncut_18.96}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump finder in
\flower during its accreting phase (\Fig{SFH}a), where \flower is dispersion-dominated (left two columns), and 
its quiescent phase, which is rotation-dominated (right two columns).
Leftmost and second left panels show the accreting phase of \flower from different viewing angles. Similarly, for the right two columns
in the quiescent phase.
Colorbar on the right shows the mean H$_2$ number density, weighted by gas mass. 
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. 
\AP{label with the phase should be included in the first row}
\label{fig:MCC}
}
\end{figure*}
